Machine Learning for Predictive Auto-Tuning with Boosted Regression Trees

### 2011-12-14 paper/draft1.tex
na

Figure~\ref{fig:allstars} shows the effectiveness of empirical auto-tuning is
in this setting.  Taking the GTX 295 as an example, and averaging across the
range of problem configurations in our study, we find that empirically
auto-tuned implementations are on average about 50\% faster than the reference
implementation.  The reference in turn, is about 50\% faster than
implementations that were empirically auto-tuned for a \emph{randomly chosen}
different argument configuration.  This shows that it is genereally not enough
to auto-tune for particular argument configurations; instead it is important to
choose the right kernel for the job for each unique argument configuration
(input-dependent auto-tuning).

>>>>

Figure~\ref{fig:allstars} shows the effectiveness of empirical auto-tuning is
in this setting.  Taking the GTX 580 as an example, and averaging across the
range of problem configurations in our study, we find that empirically
auto-tuned implementations are on average about 50\% faster than the reference
implementation.  The reference in turn, is about 50\% faster than
implementations that were empirically auto-tuned for a \emph{randomly chosen}
different argument configuration.  This shows that it is genereally not enough
to auto-tune for particular argument configurations; instead it is important to
choose the right kernel for the job for each unique argument configuration
(input-dependent auto-tuning).
